### 2017-06-30 paper.tex
Revising paper

% \newcommand{\lorem}{{\bf LOREM}}
% \newcommand{\ipsum}{{\bf IPSUM}}
\newcommand{\rulemajor}[1]{\section{#1}}

@@

\rulemajor{Clarify your audience}

@@

\rulemajor{Make lessons modular}

Every instructor's needs are different,
so build small chunks that can be re-purposed in many ways.
A university lecturer in meteorology,
for instance,
might construct a course for their students by bringing together lessons on differential equations,
fluid mechanics,
and absorption spectroscopy.
Creating courses this way shifts the instructor's burden from writing to finding and synthesizing,
which are easier if lessons clearly define what they cover (Rule~1),
and if lessons have been designed by people with a shared world-view (Rule~3).

One way to achieve this is to take existing courses and break them down into smaller, single-purpose modules
(a change which has pedagogical and administrative advantages in its own right).
When this is done,
these modules can be made more discoverable
by referencing specific points in the model curricula promulgated by many professional societies.
Smaller modules are also more approachable for new contributors (Rule~4).

\rulemajor{Teach best practices for lesson development}

@@

\rulemajor{Encourage and empower contributors}

@@

\rulemajor{Build community around lessons}

@@

A key part of doing this is to create opportunities for legitimate peripheral participation \cite{FIXME}.
Curating a list of small tasks that newcomers can easily tackle,
encouraging them to give feedback on proposed changes,
or asking them to add new exercises and tweak diagrams and references
can all provide an on-ramp for people who might question their authority or ability to change the main body of a lesson.
Equally,
acknowledging all contributions,
however small,
gives new contributors an early reward for taking part.

@@

\rulemajor{Publish periodically and recognize contributions}

@@

\rulemajor{Evaluate lessons at several scales}

@@

Pre- and post-class surveys can be used to discover larger macro-scale issues.
These often relate to the difficulty lesson developers may have
fully understanding the frame of reference of their audience,
e.g.,
assuming prior knowledge that learners do not have.
If possible,
post-class surveys should be conducted 30--60 days after class.
This delay allows people time to reflect,
meaning they are more likely to give accurate feedback on what they learned
rather than how entertained they were.

\rulemajor{Reduce, re-use, recycle}

@@

The same questions of re-use come when thinking about recycling content of a lesson,
such as images, data, figure, or code.
Does the license cover that as well?
If not,
then ask permission,
just as you would for any other material.

The converse of this rule is to license your own lessons in a similar open manner,
and to make them discoverable.
For example,
when lessons are published (Rule~6),
make sure that they have the usual keywords in their bibliographic entries
and HTML page headers.

\rulemajor{Link to other resources}

Most learners are unlikely to absorb everything there is to know about a topic
from your lesson alone.
This is partly a matter of scope---any interesting subject is too large
to fit in a single lesson---but also a matter of level and direction.
As Caulfield has argued \cite{choral-explanations},
the best resources provide a chorus of explanations
that offer many angles and approaches for any given topic,
each of which may be the best fit for a different subset of people.

Find these resources and direct learners to them at strategic points.
These resources may include textbooks,
technical documentation,
videos,
and web pages;
if a community or discussion forum exists for the topic,
be sure to include them as well.

Doing this is substantial work,
and maintaining it is even more so,
which makes building community around lessons (Rule~2) all the more important.
In particular,
it is vital to engage the learners as equal participants in that community:
they should both be able to propose updates, corrections, and additions to lessons,
and know that they are encouraged to do so (Rule~5).

\rulemajor{You can't please everyone}

No single lesson can be right for every learner.
Two people with no prior knowledge of a specific subject
may still be able to move at different speeds
because of different levels of general background knowledge.
Similarly,
lessons on ecology for learners in Utah and Florida
will probably be more relatable if they use different examples.
Equally,
no lesson development community can serve all purposes.
Some groups may prioritize rapid evolution,
while others may prefer a ``measure twice, cut once'' approach.

If there are complementary ways to explain something,
or points of view that can cohabit respectfully,
it may be possible to present them side by side.
There are good pedagogical reasons to do this
even if contributors \emph{do not} disagree:
weighing alternatives fosters higher-order thinking,
and as Caulfield has written,
the most popular online question and answer sites
are successful in part because they present a chorus of explanations
geared at different levels and needs
rather than a single one \cite{choral-explanations}.

But sometimes choices must be made.
The open source software community has wrestled with these issues for three decades,
and has evolved some best practices to address them
\cite{producing-oss}.
As discussed in Rule~5,
the first step is to have a clear governance structure and a clear, permissive license.
Minor disagreements should be discussed openly and respectfully.
If they cannot be resolved---i.e., if they turn out not to be so minor after all---then
contributors should split off and evolve the lesson in the way they see best.
(This is one of the reasons to have a permissive license.)

@@

>>>>

% \newcommand{\lorem}{{\bf LOREM}}
% \newcommand{\ipsum}{{\bf IPSUM}}
\newcommand{\rulemajor}[2]{\section{#1}\label{#2}}
\newcommand{\ruleref}[1]{Rule~\ref{#1}}

@@

\rulemajor{Clarify your audience}{audience}

@@

\rulemajor{Make lessons modular}{modular}

Every instructor's needs are different,
so build small chunks that can be re-purposed in many ways.
A university lecturer in meteorology,
for instance,
might construct a course for their students by bringing together lessons on differential equations,
fluid mechanics,
and absorption spectroscopy.
Creating courses this way shifts the instructor's burden from writing to finding and synthesizing,
which are easier if lessons clearly define what they cover (\ruleref{audience}),
and if lessons have been designed by people with a shared world-view (\ruleref{practices}).

One way to achieve this is to take existing courses and break them down into smaller, single-purpose modules
(a change which has pedagogical and administrative advantages in its own right).
When this is done,
these modules can be made more discoverable
by referencing specific points in the model curricula promulgated by many professional societies.
Smaller modules are also more approachable for new contributors (\ruleref{empower}).

\rulemajor{Teach best practices for lesson development}{practices}

@@

\rulemajor{Encourage and empower contributors}{empower}

@@

\rulemajor{Build community around lessons}{community}

@@

A key part of doing this is to create opportunities for legitimate peripheral participation.
Curating a list of small tasks that newcomers can easily tackle,
encouraging them to give feedback on proposed changes,
or asking them to add new exercises and tweak diagrams and references
can all provide an on-ramp for people who might question their authority or ability to change the main body of a lesson.
Equally,
acknowledging all contributions,
however small,
gives new contributors an early reward for taking part.

@@

\rulemajor{Publish periodically and recognize contributions}{publish}

@@

\rulemajor{Evaluate lessons at several scales}{evaluate}

@@

Pre- and post-class surveys should be used to uncover larger issues,
particularly those arising from developers not fully understanding their audience,
e.g.,
assuming prior knowledge that learners do not have.
Post-class surveys are most effective when conducted 30--90 days after class;
this gives people time to reflect,
so their feedback will more accurately reflect what they learned
rather than how entertained they were.

\rulemajor{Reduce, re-use, recycle}{rrr}

@@

The question of licensing also arises when recycling lesson components
such as images, data, figure, or code.
If the license does not cover them explicitly,
ask permission as you would for any other academic material.

The converse of this rule is to make the license for your lessons explicit and discoverable.
For example,
when lessons are published (\ruleref{publish}),
make sure that that keywords such as ``CC-BY'' appear in their bibliography entries
and HTML page headers.

\rulemajor{Link to other resources}{link}

Learners are unlikely to absorb everything they need to know about a topic from your lesson alone.
This is partly a matter of scope---any interesting subject is too large
to fit in a single lesson---but also a matter of level and direction.
As Caulfield has argued \cite{choral-explanations},
the best way to use the Internet is to provide a chorus of explanations
that offer many angles and approaches for any given topic,
each of which may be the best fit for a different set of needs.

Collaboratively-developed lessons should direct learners to these resources at strategic points.
Textbooks,
technical documentation,
videos,
web pages,
threads on Quora or mailing lists:
if a community or discussion forum exists for the topic,
it is worth including.

Doing this is substantial work,
and maintaining it is even more so,
which makes building community around lessons (\ruleref{community}) all the more important.
In particular,
it is vital to engage the learners as equal participants in that community:
they should both be able to propose updates, corrections, and additions to lessons,
and know that they are encouraged to do so (\ruleref{empower}).

\rulemajor{You can't please everyone}{everyone}

No single lesson can be right for every learner.
Two people with no prior knowledge of a specific subject
may still be able to move at different speeds
because of different levels of general background knowledge.
Similarly,
lessons on ecology for learners in Utah and Vietnam
will probably be more relatable if they use different examples.
A community may therefore maintain several differently-oriented or differently-paced lessons
on a single topic,
just as programming languages provide several different libraries for doing the same general thing
with different levels of performance and complexity.

Similarly,
no lesson development community can serve all purposes.
Some groups may prioritize rapid evolution,
while others may prefer a ``measure twice, cut once'' approach.
If there are complementary ways to explain something,
or points of view that can cohabit respectfully,
it may be possible to present them side by side.
There are good pedagogical reasons to do this
even if contributors \emph{do not} disagree:
weighing alternatives fosters higher-order thinking.

But sometimes choices must be made.
The open source software community has wrestled with these issues for three decades,
and has evolved some best practices to address them
\cite{producing-oss}.
As discussed in \ruleref{empower},
the first step is to have a clear governance structure and a clear, permissive license.
Minor disagreements should be discussed openly and respectfully.
If they turn out not to be so minor after all,
contributors should split off and evolve the lesson in the way they see best.
(This is one of the reasons to have a permissive license.)

@@

\newpage
